Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
Minor changes/fixes.

\begin{example}
\label{ex:translation}
Consider the combined signature of linear arithmetic and uninterpreted
functions $\Sigma = \Sigmalia \mathrel{\uplus} \Sigma_{\euf}$, where
%$\stypes{\Sigma_{\euf}} = \{ \typeint \}$ 
%\ct{shouldn't this be $\stypes{\Sigmalia} = \{ \typeint \}$?}
%and
% Something went wrong, let's just remove it --ajr
$\sfuns{\Sigma_{\euf}} = \{ \con{s} : { \typeint \rightarrow \typeint },\, \const{c} : { \typeint } \}$.
Let $\varphi$ be the $\Sigma$-formula
\begin{equation} \label{eq:ex-before}
\forallf{\con{s}} x : {\typeint}.\;\, \lite\bigl( x \leq 0,\; \con{s}(x) \teq 0,\;
  \con{s}( x ) \teq x + \con{s}( x - 1 ) \bigr) \wedge \con{s}( \con{c} ) > 100
\end{equation}
%
\jb{I think $x$ is a great name for a metavariable standing for a variable, but
why insist on using it for concrete variables of type int, when literature
normally uses $i, \ldots, n$ (and keeps $x$ for real numbers and such)?}
The definition of $\const{s}$ specifies that it returns the sum of the
positive integers up to $x$. The formula $\varphi$ is in definitional form with
respect to $\sfundefs{\Sigma}$ 
%\jb{correct? It said $\Sigma_u$, which was definitely wrong} 
and states that the sum of all
positive numbers up to $\const{c}$ is greater than $100$. This formula is
satisfiable with a model that interprets $\const{c}$ as $14$ or more.
Due to the universal quantifier,
current SMT techniques
%~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13,reynolds-et-al-2013}
%%% We described them in the intro. When I see references like that appear with
%%% no description, as a reader, I get all paranoid and wonder if it's the old
%%% stuff from the intro (Ge, Moura, Renoylds et al.) or if it's new stuff ---
%%% and I cannot remember numbers like [9,18,19] across sections or even
%%% paragraphs. --jb
are unable to find
a model for this formula. The signature $\extendsig{\Sigma}$ includes the type
$\fargtype{\con{s}}$ and the uninterpreted function $\farg{\con{s}}$ of type $\fargtype{\con{s}}
\rightarrow \typeint$. The result of $\conv( \varphi )$ 
is $\varphi'$ which (after simplification) is the $\extendsig{\Sigma}$-formula
%
\begin{equation} \label{eq:ex-after}
\!\begin{aligned}[c]
  & \phantom{{\wedge}\; }\bigl(
      \forall a : \fargtype{\con{s}}.\; \lite\bigl(
        \!\begin{aligned}[t]
         &  \farg{\con{s}}( a ) \leq 0,\;
          \con{s}(\farg{\con{s}}( a )) \teq 0,\;
\\[-\jot]
  & \con{s}(\farg{\con{s}}( a )) \teq \farg{\con{s}}( a ) + \con{s}( \farg{\con{s}}( a )-1 )
    \wedge \exists b : {\fargtype{\con{s}}}.\;\, \farg{\con{s}}( b ) \teq \farg{\con{s}}( a )-1 \bigr) \bigr)
\end{aligned}
\\[-\jot]
 & {\wedge}\; \bigl( \con{s}( \con{c} ) > 100 \wedge \exists a : {\fargtype{\con{s}}}.\;\, \farg{\con{s}}( a ) \teq \con{c} \bigr)
\end{aligned}
\end{equation}
%
The universal quantification in the resulting formula is over an uninterpreted
type $\fargtype{\con{s}}$, thus enabling the finite model finding
techniques by Reynolds et al.\ \cite{ReyEtAl-1-RR-13,reynolds-et-al-2013},
implemented in \cvc, to search for a finite interpretation for $\fargtype{\con{s}}$. 
Since all occurrences of the quantified variable $a$ in this formula are 
beneath applications of the uninterpreted function $\farg{\con{s}}$, 
the formula is in the essentially uninterpreted fragment,
for which Ge and de Moura \cite{GeDeM-CAV-09} provide 
a complete instantiation procedure, implemented in \ziii. 
Both
%%% Added "apparently". Or are we sure?  
% Yes, I'm planning to post the 2 versions of the benchmark on the evaluation page (when we add it) --ajr
\cvc and \ziii run indefinitely on formula~(\ref{eq:ex-before}), 
while they both produce a model for formula~(\ref{eq:ex-after}) 
within 100 milliseconds.\xend
\end{example}

@@

\begin{theorem}\label{thm:equi}
If $\varphi$ is a\/ $\Sigma$-formula that is in definitional form with respect to\/
$\sfundefs{\Sigma}$
and the set of function definitions\/ $\DDD$ corresponding to functions in
$\sfundefs{\Sigma}$ is admissible, then\/ $\varphi$ and\/ $\conv( \varphi )$ are
equisatisfiable.
\end{theorem}
\begin{proofsketch}
First, we show that if $\varphi$ is satisfied by $\Sigma$-interpretation $\I$, then $\conv( \varphi )$ is satisfied by a $\extendsig{\Sigma}$-interpretation $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all types $\tau \in \stypes{\Sigma}$ as $\tau^\I$,
all functions $\con{f} \in \sfuns{\Sigma}$ as $\con{f}^\I$,
and for each function $\con{f}$ of type $\tau_1 \times \cdots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$,
interprets $\fargtype{\con{f}}$ as a tuple of values of type $\tau_1^\I \times \cdots \times \tau_n^\I$,
and each $\fargx{\con{f}}{i}$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Note that $\J$ satisfies \emph{every} constraint of the form $\exists a : {\fargtype{\con{f}}}. ( \vecfarg{\con{f}}( a ) \teq \vec t )$,
since by our construction of $\J$ there exists an $a$ such that $a^\J = \vec t^\J$.
%By case analysis it follows that $\conv_0$ maintains the invariant that
%if $\conv_0( t\typ{\Bool}, \ppos )$ returns $( {t'}, \chi )$,
%then $\I$ satisfies $t$ if and only if $\J$ satisfies $t'$.
Since $\J$ satisfies $\varphi$, it satisfies a set of ground literals $L$ that entail $\varphi$.
Thus, $\J$ satisfies $L \cup \absconstraints( L )$, and by Lemma~\ref{lem:conv} we conclude $\J$ satisfies $\conv( \varphi )$.

@@

\begin{example}
Let us revisit the translated formula~(\ref{eq:ex-after}) from
Example~\ref{ex:translation}. 
This formula is unsatisfiable only if
formula~(\ref{eq:ex-before}) is unsatisfiable since $\fargtype{f}$ can be
interpreted as $\typeint$, and $\farg{f}$ can be interpreted as the identity
function. Conversely, we claim formula~(\ref{eq:ex-after}) is satisfiable
only if formula~(\ref{eq:ex-before}) is satisfiable, noting that the set
$\{ \forallf{\con{s}} x.\;\, \varphi_\con{s} \}$ is admissible,
where $\varphi_\con{s}$ is the formula $\lite\bigl( x \leq 0, \con{s}(x) \teq 0, \con{s}( x ) \teq x + \con{s}( x-1 ) \bigr)$.
%\ct{
%You cannot possibly mean "if and only if" in the two sentences above.
%Once I show that (1) is unsat iff (2) is unsat, I do not need to argue that
%(1) is sat iff (2) is sat. That is immediate.
%}
% You're right, changed both to "only if" --ajr
%As stated
%in the proof of Theorem~\ref{thm:equi}, the reason is that any model of
%formula~(\ref{eq:ex-after}) must satisfy a formula that is closed under
%function expansion, hence implying that formula~(\ref{eq:ex-before}) has a
%model.
%The rightmost conjunct $\exists a : {\fargtype{\con{s}}}. (\farg{\con{s}}( a ) \teq \con{c})$ 
%ensures that if $\con{s}( \con{c} ) > 100$ is a constraint that 
%formula~(\ref{eq:ex-after}) satisfying $\con{s}( \con{c} ) > 100$ also
%satisfies $\varphi_{\con{s}}[\con{c}/x]$. 
%The nested existential
%$\exists b.\;\, \farg{\con{s}}( b ) \teq \farg{\con{s}}( a )-1$ ensures that
%a similar constraint is enforced recursively: when $\varphi_{\con{s}}[t/x]$ is used in part to evaluate $\con{s}( \con{c} )$,
%any model of $\varphi_{\con{s}}[t/x]$ must also satisfy $\varphi_{\con{s}}[t-1/x]$ when $t > 0$. 
It is easy to see that any interpretation $\I$ satisfying formula~(\ref{eq:ex-after}) satisfies $L_0 \cup \absconstraints( L_0 )$,
where $L_0 = \{ \con{s}( \con{c} ) > 100 \}$, 
where $\absconstraints( L_0 )$ contains the single constraint $\exists a : {\fargtype{\con{s}}}. (\farg{\con{s}}( a ) \teq \con{c})$.
%The latter ensures that $\I$ satisfies a formula that entails both $\con{s}( \con{c} ) > 100$ and $\varphi_{\con{s}}[\con{c}/x]$.
Since $\I$ also satisfies both the translated function definition for $\con{s}$, i.e. the first conjunct of formula~(\ref{eq:ex-after}),
and $\absconstraints( L_0 )$, it must also satisfy the formula $\psi_1$:
\[
\lite\bigl( \con{c} \leq 0,\; 
            \con{s}(\con{c}) \teq 0,\;
            \con{s}(\con{c}) \teq \con{c} + \con{s}( \con{c}-1 )
            \wedge \exists b : {\fargtype{\con{s}}}.\;\, (\farg{\con{s}}( b ) \teq \con{c}-1) \bigr) \bigr)
\]
The existential $\exists b : {\fargtype{\con{s}}}.\;\, (\farg{\con{s}}( b ) \teq \con{c}-1)$ in the above formula
ensures that whenever $\I$ satisfies the set $L_1 = L_0 \cup \{ \neg \con{c} \leq 0, \con{s}(\con{c}) \teq \con{c} + \con{s}( \con{c}-1 ) \}$,
$\I$ satisfies $\absconstraints( L_1 )$ as well.
Hence, by repeated applications of this reasoning, it follows that
a model of formula~(\ref{eq:ex-after}) that interprets $\con{c}$ as $n$ must also satisfy the formula $\psi$:
%
\begin{equation} \label{eq:fun-closure}
\begin{split}
& \con{s}( \con{c} ) > 100 \wedge %\displaystyle
  \bigwedge\nolimits_{\vthinspace i=0}^{\!n-1} \bigl( \neg (\con{c}-i \leq 0) \wedge \con{s}( \con{c}-i ) \teq (\con{c}-i) + \con{s}( (\con{c}-i)-1 ) \bigr) \\[-\jot]
{\wedge}\; & \con{c}-n \leq 0 \wedge \con{s}( \con{c}-n ) \teq 0
\end{split}
\end{equation}
%
This formula is closed under function expansion
since it entails $\varphi_\con{s}[\con{c}-i/x]$ for $i = 0, \ldots, n$,
and contains (only) the $\con{s}$ applications corresponding to $\con{s}( \con{c}-i )$ for $i = 0, \ldots, n$.
Since $\varphi_\con{s}$ is an admissible definition,
there is a $\Sigma$-interpretation satisfying $\psi \wedge \forallf{\con{s}} x.\;\, \varphi_\con{s}$
which entails formula~(\ref{eq:ex-before}).\xend
\end{example}

@@

The results are shown in Figures \ref{fig:sat} and \ref{fig:unsat}.
They are divided into benchmarks triggering \emph{unsat} and \emph{sat}
responses and further into benchmarks before and after the translation $\conv$.
The raw evaluation data reveals no cases in which a solver answered
\emph{unsat} on a benchmark $\varphi$ and \emph{sat} on its
corresponding benchmark $\conv( \varphi )$, or vice versa, 
thereby corroborating Theorem~\ref{thm:equi}.
\ct{?! \emph{Theorems} do not need corroboration! 
Maybe we should say "consistently with Theorem~\ref{thm:equi}"?}

>>>>

\begin{example}
\label{ex:translation}
Consider the combined signature of linear arithmetic and uninterpreted
functions $\Sigma = \Sigmalia \mathrel{\uplus} \Sigma_{\euf}$, where
%$\stypes{\Sigma_{\euf}} = \{ \typeint \}$ 
%\ct{shouldn't this be $\stypes{\Sigmalia} = \{ \typeint \}$?}
%and
% Something went wrong, let's just remove it --ajr
$\sfuns{\Sigma_{\euf}} = \{ \con{s} : { \typeint \rightarrow \typeint },\, \const{c} : { \typeint } \}$.
Let $\varphi$ be the $\Sigma$-formula
\begin{equation} \label{eq:ex-before}
\forallf{\con{s}} x : {\typeint}.\;\, \lite\bigl( x \leq 0,\; \con{s}(x) \teq 0,\;
  \con{s}( x ) \teq x + \con{s}( x - 1 ) \bigr) \wedge \con{s}( \con{c} ) > 100
\end{equation}
%
\jb{I think $x$ is a great name for a metavariable standing for a variable, but
why insist on using it for concrete variables of type int, when literature
normally uses $i, \ldots, n$ (and keeps $x$ for real numbers and such)?}
\ajr{To me, $n$ typically refers to some concrete numeral, e.g. $14$.  The reason I changed the instance above is to be consistent with Example 2, which I noticed was using $x$ (and also uses $n$ to refer to a concrete numeral). So, I think I'd still prefer $x$ here.}
The definition of $\const{s}$ specifies that it returns the sum of the
positive integers up to $x$. The formula $\varphi$ is in definitional form with
respect to $\sfundefs{\Sigma}$ 
%\jb{correct? It said $\Sigma_u$, which was definitely wrong} 
and states that the sum of all
positive numbers up to $\const{c}$ is greater than $100$. This formula is
satisfiable with a model that interprets $\const{c}$ as $14$ or more.
Due to the universal quantifier,
current SMT techniques
%~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13,reynolds-et-al-2013}
%%% We described them in the intro. When I see references like that appear with
%%% no description, as a reader, I get all paranoid and wonder if it's the old
%%% stuff from the intro (Ge, Moura, Renoylds et al.) or if it's new stuff ---
%%% and I cannot remember numbers like [9,18,19] across sections or even
%%% paragraphs. --jb
are unable to find
a model for this formula. The signature $\extendsig{\Sigma}$ includes the type
$\fargtype{\con{s}}$ and the uninterpreted function $\farg{\con{s}}$ of type $\fargtype{\con{s}}
\rightarrow \typeint$. The result of $\conv( \varphi )$ 
is $\varphi'$ which (after simplification) is the $\extendsig{\Sigma}$-formula
%
\begin{equation} \label{eq:ex-after}
\!\begin{aligned}[c]
  & \phantom{{\wedge}\; }\bigl(
      \forall a : \fargtype{\con{s}}.\; \lite\bigl(
        \!\begin{aligned}[t]
         &  \farg{\con{s}}( a ) \leq 0,\;
          \con{s}(\farg{\con{s}}( a )) \teq 0,\;
\\[-\jot]
  & \con{s}(\farg{\con{s}}( a )) \teq \farg{\con{s}}( a ) + \con{s}( \farg{\con{s}}( a )-1 )
    \wedge \exists b : {\fargtype{\con{s}}}.\;\, \farg{\con{s}}( b ) \teq \farg{\con{s}}( a )-1 \bigr) \bigr)
\end{aligned}
\\[-\jot]
 & {\wedge}\; \bigl( \con{s}( \con{c} ) > 100 \wedge \exists a : {\fargtype{\con{s}}}.\;\, \farg{\con{s}}( a ) \teq \con{c} \bigr)
\end{aligned}
\end{equation}
%
The universal quantification in the resulting formula is over an uninterpreted
type $\fargtype{\con{s}}$, thus enabling the finite model finding
techniques by Reynolds et al.\ \cite{ReyEtAl-1-RR-13,reynolds-et-al-2013},
implemented in \cvc, to search for a finite interpretation for $\fargtype{\con{s}}$. 
Since all occurrences of the quantified variable $a$ in this formula are 
beneath applications of the uninterpreted function $\farg{\con{s}}$, 
the formula is in the essentially uninterpreted fragment,
for which Ge and de Moura \cite{GeDeM-CAV-09} provide 
a complete instantiation procedure, implemented in \ziii. 
Both
%%% Added "apparently". Or are we sure?  
% Yes, I'm planning to post the 2 versions of the benchmark on the evaluation page (when we add it) --ajr
\cvc and \ziii run indefinitely on formula~(\ref{eq:ex-before}), 
while they both produce a model for formula~(\ref{eq:ex-after}) 
within 100 milliseconds.\xend
\end{example}

@@

\begin{theorem}\label{thm:equi}
If $\varphi$ is a\/ $\Sigma$-formula that is in definitional form with respect to\/
$\sfundefs{\Sigma}$
and the set of function definitions\/ $\DDD$ corresponding to functions in
$\sfundefs{\Sigma}$ is admissible, then\/ $\varphi$ and\/ $\conv( \varphi )$ are
equisatisfiable.
\end{theorem}
\begin{proofsketch}
First, we show that if $\varphi$ is satisfied by $\Sigma$-interpretation $\I$, then $\conv( \varphi )$ is satisfied by a $\extendsig{\Sigma}$-interpretation $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all types $\tau \in \stypes{\Sigma}$ as $\tau^\I$,
all functions $\con{f} \in \sfuns{\Sigma}$ as $\con{f}^\I$,
and for each function $\con{f}$ of type $\tau_1 \times \cdots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$,
interprets $\fargtype{\con{f}}$ as a tuple of values of type $\tau_1^\I \times \cdots \times \tau_n^\I$,
and each $\fargx{\con{f}}{i}$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Since $\J$ satisfies $\varphi$, it satisfies a set of ground literals $L$ that entail $\varphi$.
Furthermore, $\J$ satisfies \emph{every} constraint of the form $\exists a : {\fargtype{\con{f}}}. ( \vecfarg{\con{f}}( a ) \teq \vec t )$,
since by our construction of $\J$ there exists an $a$ such that $a^\J = \vec t^\J$.
%By case analysis it follows that $\conv_0$ maintains the invariant that
%if $\conv_0( t\typ{\Bool}, \ppos )$ returns $( {t'}, \chi )$,
%then $\I$ satisfies $t$ if and only if $\J$ satisfies $t'$.
Thus, $\J$ satisfies $L \cup \absconstraints( L )$, and by Lemma~\ref{lem:conv} we conclude $\J$ satisfies $\conv( \varphi )$.

@@

\begin{example}
Let us revisit the translated formula~(\ref{eq:ex-after}) from
Example~\ref{ex:translation}. 
This formula is unsatisfiable only if
formula~(\ref{eq:ex-before}) is unsatisfiable since $\fargtype{f}$ can be
interpreted as $\typeint$, and $\farg{f}$ can be interpreted as the identity
function. Conversely, we claim formula~(\ref{eq:ex-after}) is satisfiable
only if formula~(\ref{eq:ex-before}) is satisfiable, noting that the set
$\{ \forallf{\con{s}} x.\;\, \varphi_\con{s} \}$ is admissible,
where $\varphi_\con{s}$ is the formula $\lite\bigl( x \leq 0, \con{s}(x) \teq 0, \con{s}( x ) \teq x + \con{s}( x-1 ) \bigr)$.
%\ct{
%You cannot possibly mean "if and only if" in the two sentences above.
%Once I show that (1) is unsat iff (2) is unsat, I do not need to argue that
%(1) is sat iff (2) is sat. That is immediate.
%}
% You're right, changed both to "only if" --ajr
%As stated
%in the proof of Theorem~\ref{thm:equi}, the reason is that any model of
%formula~(\ref{eq:ex-after}) must satisfy a formula that is closed under
%function expansion, hence implying that formula~(\ref{eq:ex-before}) has a
%model.
%The rightmost conjunct $\exists a : {\fargtype{\con{s}}}. (\farg{\con{s}}( a ) \teq \con{c})$ 
%ensures that if $\con{s}( \con{c} ) > 100$ is a constraint that 
%formula~(\ref{eq:ex-after}) satisfying $\con{s}( \con{c} ) > 100$ also
%satisfies $\varphi_{\con{s}}[\con{c}/x]$. 
%The nested existential
%$\exists b.\;\, \farg{\con{s}}( b ) \teq \farg{\con{s}}( a )-1$ ensures that
%a similar constraint is enforced recursively: when $\varphi_{\con{s}}[t/x]$ is used in part to evaluate $\con{s}( \con{c} )$,
%any model of $\varphi_{\con{s}}[t/x]$ must also satisfy $\varphi_{\con{s}}[t-1/x]$ when $t > 0$. 
It is easy to see that any interpretation $\I$ satisfying formula~(\ref{eq:ex-after}) satisfies $L_0 \cup \absconstraints( L_0 )$,
where $L_0 = \{ \con{s}( \con{c} ) > 100 \}$, 
where $\absconstraints( L_0 )$ is the set consisting of the single constraint $\exists a : {\fargtype{\con{s}}}. (\farg{\con{s}}( a ) \teq \con{c})$.
%The latter ensures that $\I$ satisfies a formula that entails both $\con{s}( \con{c} ) > 100$ and $\varphi_{\con{s}}[\con{c}/x]$.
Since $\I$ also satisfies both the translated function definition for $\con{s}$, i.e. the first conjunct of formula~(\ref{eq:ex-after}),
and $\absconstraints( L_0 )$, it must also satisfy the formula $\psi_1$:
\[
\lite\bigl( \con{c} \leq 0,\; 
            \con{s}(\con{c}) \teq 0,\;
            \con{s}(\con{c}) \teq \con{c} + \con{s}( \con{c}-1 )
            \wedge \exists b : {\fargtype{\con{s}}}.\;\, (\farg{\con{s}}( b ) \teq \con{c}-1) \bigr) \bigr)
\]
The existential $\exists b : {\fargtype{\con{s}}}.\;\, (\farg{\con{s}}( b ) \teq \con{c}-1)$ in the above formula
ensures that whenever $\I$ satisfies the set $L_1 = L_0 \cup \{ \neg \con{c} \leq 0, \con{s}(\con{c}) \teq \con{c} + \con{s}( \con{c}-1 ) \}$,
$\I$ satisfies $\absconstraints( L_1 )$ as well.
Hence, by repeated applications of this reasoning, it follows that
a model of formula~(\ref{eq:ex-after}) that interprets $\con{c}$ as $n$ must also satisfy the formula $\psi$:
%
\begin{equation} \label{eq:fun-closure}
\begin{split}
& \con{s}( \con{c} ) > 100 \wedge %\displaystyle
  \bigwedge\nolimits_{\vthinspace i=0}^{\!n-1} \bigl( \neg (\con{c}-i \leq 0) \wedge \con{s}( \con{c}-i ) \teq (\con{c}-i) + \con{s}( (\con{c}-i)-1 ) \bigr) \\[-\jot]
{\wedge}\; & \con{c}-n \leq 0 \wedge \con{s}( \con{c}-n ) \teq 0
\end{split}
\end{equation}
%
This formula is closed under function expansion
since it entails $\varphi_\con{s}[\con{c}-i/x]$ for $i = 0, \ldots, n$,
and contains only $\con{s}$ applications corresponding to $\con{s}( \con{c}-i )$ for $i = 0, \ldots, n$.
Since $\varphi_\con{s}$ is an admissible definition,
there is a $\Sigma$-interpretation satisfying $\psi \wedge \forallf{\con{s}} x.\;\, \varphi_\con{s}$
which entails formula~(\ref{eq:ex-before}).\xend
\end{example}

@@

The results are shown in Figures \ref{fig:sat} and \ref{fig:unsat}.
They are divided into benchmarks triggering \emph{unsat} and \emph{sat}
responses and further into benchmarks before and after the translation $\conv$.
The raw evaluation data reveals no cases in which a solver answered
\emph{unsat} on a benchmark $\varphi$ and \emph{sat} on its
corresponding benchmark $\conv( \varphi )$, or vice versa.
This is consistent with our expectations and Theorem~\ref{thm:equi}, 
since these benchmarks contained only sets of function definitions that we expected were admissible.
%thereby confirming Theorem~\ref{thm:equi}.
%\ct{?! \emph{Theorems} do not need corroboration! 
%Maybe we should say "consistently with Theorem~\ref{thm:equi}"?}
